---
title: "Programming Background"
author: "Mark Gordon"
date: '2022-06-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
```

## R as a programming language

R and SAS are both great statistical tools and they both have their pluses and minuses.  SAS I've found tends to have a lot better default tools for the statistics themselves.  However, R is much easier to customize the output for things like plots.  One of my previous professors said he'll often do the statistical calculations using SAS but generate plots in R.  This feels like something I might do myself as SAS plots are customizable, but less intuitively so.  

The parts I missed about SAS were things like the ease of doing an iterative finding of which variables to use.  While there is a package for this in R, it didn't really do it in the same way and didn't follow the rules of analysis (such as requiring the linear term for quadratic or interaction terms).  I didn't find R particularly difficult to learn.  At least, not base R.  Some of the packages such as ggplot2 have a good bit of a learning curve, at least when I tried to teach it to myself during ST503.

## R Markdown output

```{r}
plot(iris)
```

<!-- rmarkdown::render("_Rmd/2022-06-08-programming-background.Rmd", output_format = "github_document", output_dir = "_posts", output_options = list(html_preview = "false")) -->